\textls[-0]{\thetitle}

### 2023-03-14 metatheory2.tex
Attach universe level. And Fix.

Finally, $\SubstWeak{n}$ is a short hand for $\pi_1^n~"id"$ and $\var{n}$ is a short hand for $\pi_2~\pi_1^{n}$. Thus during meta-theoretic reasoning, we will only deal with $\pi_1$ and $\pi_2$.

>>>>

To simplify, $\SubstWeak{n}$ is a short hand for $\pi_1^n~"id"$ and $\var{n}$ is a short hand for $\pi_2~\pi_1^{n}$. Thus during meta-theoretic reasoning, we will only deal with $\pi_1$ and $\pi_2$.

Finally, we have \ruleref{sub/dbj/shift} defined using \ruleref{sub/wk} and \ruleref{tm/var}. This rule applying substitution $\gm$ on the earlier part of the context. We usually omit $A$ in the $\gm^{\uparrow A}$ because it can be inferred from the context.
